### 2018-05-15 General WLD combinatorics.tex
Some changes made to section 3. proof of cyclic intervals is broken.

\begin{proof}
If two maximal triangulated pieces were not disjoint, then one could take the union of the edges involved to get a larger triangulated piece. \note{Is it this simple? This is a variant of the proof on propagators}
\end{proof}

@@

Let $\interval{1}{n}$ denote the set of integers $\{1,2, \dots, n\}$, and $\binom{[n]}{k}$ the set of all $k$-subsets of $\interval{1}{n}$.  For each $j \in \interval{1}{n}$, we can define a total order $\leq_j$ on the interval $\interval{1}{n}$ by
\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1.\]
This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.  It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order}), which is defined as follows: if $A = [a_1 <_j a_2 <_j \dots <_j a_k]$,  $B = [b_1 <_j b_2 <_j \dots <_j b_k] \in \binom{[n]}{k}$, then
\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
For example, in $\binom{[6]}{3}$ we have $[2,5,6]\gale{2} [2,6,1]$ but $[2,5,6]\not\gale{2}[3,4,6]$.

@@

By [ref], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $Gr(k,n)^{tnn}$.  Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in \interval{1}{n}$:
\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in \interval{1}{n}\right\}.\]
We now describe an algorithm that, when applied to an admissible Wilson loop diagram, produces exactly the Grassmann necklace of the corresponding positroid.

\begin{algorithm}\label{alg:put GN on WLD}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Note that whenever the algorithm below refers to the ``rightmost'' propagator supported on a vertex $i$, we mean the rightmost from the point of view of standing in the middle of the diagram and looking directly at $i$.

\begin{enumerate}
\item Fix a vertex $s \in \interval{1}{n}$, and set $i:=s$.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $s$}: If there is at least one propagator in the current diagram supported on $i$, add the label $i$ to the edge $(s,s+1)$ and delete the rightmost propagator supported on $i$; otherwise do nothing.
\item If there are no propagators left in the diagram at this point, go to (2) below.
\item Otherwise, increment $i$ by 1 and repeat from (a).
\end{enumerate}
\item Replace all propagators in the diagram, and repeat from (1) for a new vertex $s$.  Continue until the algorithm has been applied to all vertices.
\end{enumerate}
\end{algorithm}

\begin{prop}\label{res:alg k labels}
If $W$ is an admissible Wilson loop diagram, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop}
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each vertex.  Suppose this doesn't happen, i.e. there is a propagator $P$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.  We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.

Rotating and cyclically renumbering if necessary, we can assume that $s=1$ and that $P$ is supported on $(a,a+1,b,b+1)$ with $1 \leq a < b$.  Since $P$ is not removed at step $b+1$, there is another propagator $p_1$ to its right which is also supported on $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
\end{proof}

To prove that this algorithm gives the Grassmann necklace of the diagram we need two lemmas.

@@

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item $R$ is the radical of $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.

The final thing to prove for this item is that there are no irreducible factors $f$ of degree 3 or more.  Now suppose for a contradiction that $f$ has degree $\geq 3$. Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and $i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.

Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.  These are illustrated in Figure~\ref{fig no big factors}

\begin{figure}
  \includegraphics{no_big_factors}
  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
\end{figure}

\textbf{Case I}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.  Then $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.  Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}  The construction of $I_{i+1}$ begins as for $I_i$ after the first step; they can only differ once $p$ contributes to $I_{i+1}$.  Thus if a propagator contributes $m$ in $I_i$ then it cannot be a propagator inside $p$ (nor $p$ itself).  Let $S$ be the set of propagators inside $p$ along with $p$ itself.  Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$ which is a contradiction.  The other thin which can happen is that at least one of $m$ and $m+1$ is in $I_i$.  However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$ which is square of size $|S|\times |S|$. No other propagators can be supported on these vertices since all other propagators are outside of $p$ and $p$ is the first propagator supported at $i$.  This explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$ and both factors are nontrivial since $m$ appears in $I_i$.  If we remove the propagator outside of $p$ we get a smaller diagram for which $\Delta_{I_i} = \det A$, this contradicts the minimality of our choices unless $\det A$ is quadratic which in turn contradicts that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.

\textbf{Case II}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column for vertex $i$ has only one nonzero entry in it and so $\Delta_{I_i}$ has a linear factor which is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$ and we know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction.  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case I, in particular $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes it is outside of $q$.  Thus similarly to case I, if we let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves then all propagators in $S$ are mapped by $I_i$ to vertices strictly before $j$ and no other propagators cover vertices strictly before $j$.  Thus the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$. Again two things can now happen.  If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.  Hence, as in case I either this contradicts minimality by removing those propagators not contributing to $A$, or $\det A$ is quadratic which contradicts that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.  On the other hand, if no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.  Looking in more detail into $A$, note that of supports of $p$ and $q$, only $i$ and $i+1$ are in $I_i$ and hence
\[
A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
\]
where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.  Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$ contradicting our assumptions.

All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.

    \item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.  For any fixed bijection $\sigma$ of the propagators other than $p$ and $q$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways, either $p\rightarrow a$ and $q\rightarrow b$ or $p\rightarrow b$ and $q\rightarrow a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is the product of the minor of $C(W)$ coming from $p, q$ and $a,b$ with the minor coming from the other propagators and $I_i - \{a,b\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_1x_4-x_2x_3$ is a factor of $\Delta_{I_i}$.

Now let $f$ be a quadratic factor of $\Delta_{I_i}$.  By the previous part we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.  It remains to show that $a$ and $b$ are adjacent.  From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.

As in the proof of the previous part, make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.  The cases in the proof of the previous part show how $\Delta_{I_i}$ factors; in particular the vertices covering the second end of $p$ either do not appear in $I_i$ or contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.  By assumption $b$ contributes to the same factor as $a$.  Therefore $(a,b)$ is an edge.
    \item
    \item
  \end{enumerate}
\end{proof}

>>>>

\begin{proof}
Consider any two disctinct maximal triangulations of $\tau(W)$. These two triangulations correspond to subtrees of $T(W)$. These subtrees intersect, at most, at a vertex in an interior of $\tau(W)$. Since the subtrees corresponding to the maximal subtrees are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulations to be edge disjoint as well.
\end{proof}

@@

Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
\bas j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\eas
This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.  It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order}), which is defined as follows: if $A = [a_1 <_j a_2 <_j \dots <_j a_k]$,  $B = [b_1 <_j b_2 <_j \dots <_j b_k] \in \binom{[n]}{k}$, then
\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
For example, in $\binom{[6]}{3}$ we have $[2,5,6]\gale{2} [2,6,1]$ but $[2,5,6]\not\gale{2}[3,4,6]$.

@@

By [ref], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $Gr(k,n)^{tnn}$.  Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
We now describe an algorithm that, when applied to an admissible Wilson loop diagram, produces exactly the Grassmann necklace of the corresponding positroid.

\begin{algorithm}\label{alg:put GN on WLD}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.

\begin{enumerate}
\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $s$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$. Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$. Write $W = (\cP \setminus p, n)$.
\item If $Prop(i) = \emptyset$ do nothing.
\item Increment $i$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm} \note{I don't like how this is written. Any ideas?}

\begin{prop}\label{res:alg k labels}
If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop} \note{is there a way to do this theorem using the chords and polygons?}
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$. In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$. Suppose this doesn't happen, i.e. there is a propagator $p_0 \in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.  We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.

Fix an $a \in [n]$. Write $V_{p_0} = (i_{p_0},i_{p_0}+1,j_{p_0},j_{p_0}+1)$ with $a \leq_a i_{p_0} <_a j_{p_0}$.

Since $p$ is not removed by step $j_{p_0}+1$, there are $4$ propagators $q_1, r_1, s_1, t_1$ that are removed at step $i_{p_0},i_{p_0}+1,j_{p_0}$ , or $j_{p_0}+1$ respectively, allowing $p_0$ to remain after $n$ steps. Let us consider the propagators $s_1$ and $t_1$, preventing $p_0$ from being eliminated at steps $b_0$ and $b_0+1$. Let $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$, where \bas i_{p_0} <_a i_{t_1} <_a i_{s_1} < j_{s_1} \leq_a j_{t_1} = j_{p_0}\;.\eas Note that $j_{r_1}$ must either be $j_{p_0}-1$ or $j_{p_0}$. Otherwise, it would not be removed at the $j_{p_0}^{th}$ step. Admissibility prevents $i_{p_0} = i_{t_1}$ as this would imply that both $p_0 = (i_{p_0}, j_{p_0})$ and $t_1 = (i_{p_0}, j_{p_0})$.

In order for $t_1$ and $s_1$ to be removed at step $j_{p_0}$ and $j_{p_0}+1$ respectively, they cannot be removed at steps $i_{t_1}$ and $i_{t_1} +1$ or $i_{s_1}$ and $i_{s_1}+1$ respectively. Therefore, there needs to be two pairs of propagators, $q_2$, $r_2$ which are removed at step $i_{s_1}$ and $i_{s_1}+1$, and $q_3$, $r_3$ which are removed at step $i_{t_1}$ and $i_{t_1}+1$. Note that this implies that $i_{p_0}+2 <_a i_{t_1}$. Otherwise, there is not room to place both the propagators $q_3$, $r_3$.

For each $q_m$ and $r_m$ thus identified, there must be other pairs of propagators, $p_{m'}$ and $q_{m'}$ (with $m'> m$) that are removed at steps $i_{q_m}$ and $i_{q_m} +1$ or $i_{r_m}$ and $i_{r_m}+1$. Note that under this construction, $i_{r_m} <_a i_{q_m}$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction ($p_k \in \{q_k, r_k, s_k, t_k\}$, or $k=0$).

 \begin{description}
\item[$i_{r_m} = i_{p_k}+2$] Then there is not room to place both the propagators $q_{m'}$, and $r_{m'}$. Thus $r_m$ is removed at the step $i_{r_m} + 1$. Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
 \item[$i_{r_m} = i_{p_k}+1$] Then there is not room to place either the propagators $q_{m'}$, and $r_{m'}$. Thus $r_m$ is removed at the step $i_{r_m}$. Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
 \item[$i_{r_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $q_m$ is not removed at $i_{q_m}$ or $i_{q_m}+1$. By the above argument, there exists an $r_{m'}$ such that $i_{r_m'} = i_{r_m}$. This requires the existence of propagators that that $q_m'$ is not removed at $i_{q_m'}$ or $i_{q_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{q_m} - i_{r_m}-1$ propagators can be supported on the cyclic interval $\{i_{r_m}, i_{q_m}+1\}$.
 \end{description}

\todo{can this be simplified? Does it just need a picture?}

\begin{comment}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
\end{comment}
\end{proof}

Infact, we have proved more than the fact that each propagator contributes to the $I_a$ by the $n^{th}$ step. We have shown the each vertex $v \in V_p$ is contributed to some $I_{a_{p,v}}$ by $p$ for some $a_{p,v} \in [n]$

\begin{cor}\label{every vertex contributed cor}
For each propagator $p \in \cP$, and vertex $v \in V_p$, there is an $a_{p,v}$ such that $p$ contributes $v$ to $I_{a_{p,v}}$.
\end{cor}

\begin{proof}
Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.

Suppose $p$ never contributed $j$ via Algorithm \ref{alg:put GN on WLD}. There there would be at least one propagator $s_1 = (i_{s_1}, j_{s_1})$ that contributed $j$ for all vertices $a \in [n]$. The vertex $j_{s_1} \in \{j, j-1\}$. Then there would have to be propagators $q_2$, $r_2$ that contributed $i_{s_1}$ and $i_{s_2}$ for all $a \in [n]$. But this is would create the need for an infinite number of propagators in a finite Wilson Loop diagram, which is impossible.

The same argument holds for $j+1$, except that one has to add the existence of a second propagator $t_1 = (i_{t_1}, j)$ to the construction above.

By cyclic symmetry, this is sufficient to prove that $p$ must also contribute $i$ and $i+1$ at some point.

For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram. Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$. Furthermore, for any $p = (i, j) \in \cP$, write $\cP_{i,j} =  \{ q = (i_q, j_q)\in \cP | i \leq_i i_q <_i j_q \leq_i j\}$ to be the set of propagators supported on the cyclic interval $[i, j]$. Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$. Note that $p = \cP_{i,j} \cap \cP_{j,i}$.

We then have the following corrollary:

\begin{cor} \label{rightmost prop last cor}
Given any Wilson loop diagram, $W = (\cP, n)$, and $p = (i,j) \in \cP$, consider the subdiagrams $W_L  = (\cP_{i,j}, n)$ and $W_R = (\cP_{j,i}, n)$. Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
\end{cor}

\begin{proof}
Consider $W_L$. Since every propagator in a Wilson loop diagram must contribute to $I_{i+2}^{W_L}$, it remains to check that no propagator can contribute after $p$. This could only happen if there were a different propagator, $q$ with an endpoint on edge $i$. If $q = (i , i+2)$, then it would be the first propagators to be removed, with contribution $i+2$. If it $q = (i, l)$, with $l > i+2$, then it would contribute either $l$ or $l+1$. Otherwise, one would need the existence of an infinite set of other propagators, as above.

A similar argument works for $W_R$. 
\end{proof}

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, there is a cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
\end{lem}

\begin{proof}

Fix $p \in \cP$, with $p = (i,j)$. Consider two subsets of propagators in $\cP$, $Q = \{q_m\}$, $R = \{r_n\}$. Let $Q \subseteq \cP_{i,j}$ be the set of propagators with one end point either on the edge $j-1$ or $j$. Label the other endpoint of $q_m$ as the edge $k_m$, with $i \leq_i k_1 <_i k_2 <_i \ldots \leq_i j$. In other words, they are ordered from closest to furthest away from $p$.

Similarly, define $R \subset \cP_{j,i}$ be the set of propagators with one end point either on the edge $i-1$ or $i$. I label the other endpoint of $r_n$ as the edge $l_n$, with $j \leq_j l_1 <_j l_2 <_j \ldots \leq_j i$. In other words, they are ordered from closest to furthest away from $p$.

\todo{Insert picture here}

For any $m >|Q|$ (resp. $m > |R|$), write $k_m= j$ (resp. $l_n = i$).

We make the following four claims:

\begin{enumerate}
\item The propagator $p$ contributes $i$ for all $I_a$ for $a \in [a_{p,i} = k_2+2, b_{p,i} = l_1+1]$ 
\item The propagator $p$ contributes $i+1$ for all $I_a$ for $a \in [b_{p,i} +1, a_{p, j} -1]$. 
\item The propagator $p$ contributes $j$ for all $I_a$ for $a \in [a_{p,j} = l_2+2, b_{p,j} = k_1+1 ]$
\item The propagator $p$ contributes $j+1$ for all $I_a$ for $a \in [k_1+2, k_2+1 ]$
\end{enumerate}

This proof follows from the argument in Corollary \ref{rightmost prop last cor}, and Corrollary \ref{every vertex contributed cor} that show that $p$ contributes last to $I_{i+2}^{W_L}$. In particular, $p$ contributes after all the propagators in $Q$ in $I_{i+2}$. Furthermore, it contributes either $j$ or $j+1$ to this entry. If $q_1 \neq (k_1 = i, j-1)$, then $p$ contributes $j$. This is because $i+2 \leq_i k_m+1$ for all $m > 0$, which forces the propagators $q_m$ to contribute at the $k_m$ or $k_m+1$ vertex.

\note{there seems to be a problem with the proof as written, namely, it isn't consistent with itself if you change from $p$ to $q_1$.}

@@

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item $R$ is the radical of $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

Now suppose for a contradiction that $f$ has degree $\geq 3$. \note{This is where I'm working next and maybe the result isn't true.  I will send you an example unless I figure it out myself.}

    \item
    \item
    \item
  \end{enumerate}
\end{proof}
